Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe--Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v2.2)} \underline{Drafting Committee: DC90 (\today)}

### 2012-01-13 results_dual.tex

\section{Results}
\red{The results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work and results extracted in Ref.~\cite{fd} from the previously published 1996-2005 data set} are compared in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster_dual}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the \red{uncertainty} of
the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

A statistical test \red{(Student's test)} was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets. Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated\red{, i.e. effects from detector resolution, acceptance and smearing}. This test revealed no significant evidence for incompatibility between the data sets. The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the \red{entire} hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual_update_1.pdf}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of
the beam polarisation measurement. Solid and dashed lines show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_cluster_update_withassoc_dual}
    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007. The error bars (bands) represent the statistical (systematic) uncertainties.  Theoretical calculations from the model described in Ref. \cite{Kum09} are shown as solid and dashed lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bca_xbjrange}
 \end{center}
\end{figure}

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_dual}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of the beam polarisation measurement.}
  \label{bsa_xbjrange2}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_tc_xbjrange_withfrac.pdf}
    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties.}
  \label{bca_xbjrange2}
 \end{center}
\end{figure}

>>>>

\section{Results}
\red{The results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work and results extracted in Ref.~\cite{fd} from the previously published 1996-2005 data set} are compared in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{macros/bsa_both_morgan}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the \red{uncertainty} of
the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

A statistical test \red{(Student's test)} was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets. Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated\red{, i.e. effects from detector resolution, acceptance and smearing}. This test revealed no significant evidence for incompatibility between the data sets. The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the \red{entire} hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{macros/bca_both_morgan}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{macros/morgan_change}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of
the beam polarisation measurement. Solid and dashed lines show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{macros/morgan_change2}
    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007. The error bars (bands) represent the statistical (systematic) uncertainties.  Theoretical calculations from the model described in Ref. \cite{Kum09} are shown as solid and dashed lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bca_xbjrange}
 \end{center}
\end{figure}

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{macros/bsa_2d_morgan}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of the beam polarisation measurement.}
  \label{bsa_xbjrange2}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{macros/bca_2d_morgan}
    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties.}
  \label{bca_xbjrange2}
 \end{center}
\end{figure}
